surfing

### 2021-05-04 inst/surfing.Rmd
more work, exclude wildcards and Vries

```{r}
head(read.table("players.txt",header=TRUE))
```

@@

The first line shows that, at one of the heats in `wct01`, `Colapinto`
came first, `Bailey` second, and `Wright` came third.  The last line
shows that, at `wct11`, `Ferreira` came first and `Medina` came
second.  We can convert this dataset into a Plackett-Luce likelihood
function as follows:

```{r definerowing, cache=TRUE}

surfing <- hyper2()
for(v in o){surfing <- surfing + race(v[-1])} # first entry is venue
summary(surfing)
```

>>>>

```{r}
players <- read.table("players.txt",header=TRUE)
head(players)
table(players$nation)
players$name
wildcards <- players$name[-(1:36)]
wildcards
```

@@

The first line shows that, at one of the heats in `wct01`, `Colapinto`
came first, `Bailey` second, and `Wright` came third.  The last line
shows that, at `wct11`, `Ferreira` came first and `Medina` came
second.  We can convert this dataset into a Plackett-Luce likelihood
function but first have to remove the wildcards and also player Vries
whose maximum likelihood strength is zero.

```{r definesurfing, cache=TRUE}
remove <- c(wildcards, "Vries")
surfing <- hyper2()
for(v in o){
   r <- v[-1]  # first entry is venue
   numberretained <- sum(!(r %in% remove))
   if(numberretained > 1){
     r <- r[!(r %in% remove)]
     surfing <- surfing + race(r)
    }
}	
summary(surfing)
```
